---
title: "California Wildfire Prediction"
author: "Hui Tian & Jiali Yao"
date: "11/29/2021"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 10
    fig_height: 9
    theme: united
    highlight: tango
---
# I Introduction

California wildfires

```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(error = FALSE)

# Hui Local Folder
#setwd("C:\\PENN\\2021\\MUSA_508_PublicPolicy\\Final_Project")

# Jialli Local Folder
setwd("D:\\graduate\\MUSA508\\ASSIGNMENT\\Final\\MUSA_508_Final")


# LIBRARIES
library(rjson)
library(tidycensus)
library(tidyverse)
library(sf)
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(grid)
library(gridExtra)
library(ggcorrplot)
library(jtools)  
library(viridis)
library(kableExtra)
library(rlist)
library(dplyr)
library(osmdata)
library(geosphere)
library(fastDummies)
library(FNN)
library(viridis)
library(stargazer)
library(pscl)
library(pROC)
library(plotROC)
library(RANN)
library(riem)
options(scipen=999)
options(tigris_class = "sf")

# THEMES AND FUNCTIONS
mapTheme <- function(base_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = 14,colour = "black"),
    plot.subtitle=element_text(face="italic"),
    plot.caption=element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),axis.title = element_blank(),
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=2)
  )
}

plotTheme <- function(base_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = 14,colour = "black"),
    plot.subtitle = element_text(face="italic"),
    plot.caption = element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),
    panel.grid.major = element_line("grey80", size = 0.1),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=2),
    strip.background = element_rect(fill = "grey80", color = "white"),
    strip.text = element_text(size=12),
    axis.title = element_text(size=12),
    axis.text = element_text(size=10),
    plot.background = element_blank(),
    legend.background = element_blank(),
    legend.title = element_text(colour = "black", face = "italic"),
    legend.text = element_text(colour = "black", face = "italic"),
    strip.text.x = element_text(size = 14)
  )
}

# PALETTE
palette2 <- c("#F96167","#FCE77D")

qBr <- function(df, variable, rnd) {
  if (missing(rnd)) {
    as.character(quantile(round(df[[variable]],0),
                          c(.01,.2,.4,.6,.8), na.rm=T))
  } else if (rnd == FALSE | rnd == F) {
    as.character(formatC(quantile(df[[variable]]), digits = 3),
                 c(.01,.2,.4,.6,.8), na.rm=T)
  }
}

q5 <- function(variable) {as.factor(ntile(variable, 5))}

# FUNCTIONS
nn_function <- function(measureFrom,measureTo,k) {
  measureFrom_Matrix <- as.matrix(measureFrom)
  measureTo_Matrix <- as.matrix(measureTo)
  nn <-   
    get.knnx(measureTo, measureFrom, k)$nn.dist
  output <-
    as.data.frame(nn) %>%
    rownames_to_column(var = "thisPoint") %>%
    gather(points, point_distance, V1:ncol(.)) %>%
    arrange(as.numeric(thisPoint)) %>%
    group_by(thisPoint) %>%
    summarize(pointDistance = mean(point_distance)) %>%
    arrange(as.numeric(thisPoint)) %>% 
    dplyr::select(-thisPoint) %>%
    pull()
  
  return(output)  
}
```
# II Load Data

### 2.1 Load data of California wildfires


```{r load data, message=FALSE, warning=FALSE, cache=TRUE, results=FALSE}
# California Counties

ca_counties <- st_read("https://opendata.arcgis.com/datasets/a61c138d0a6946da8d1ebb8d1c9db13a_0.geojson")%>%
  st_transform('EPSG:2225')


# Fire Perimeter

fire <- st_read("https://services1.arcgis.com/jUJYIo9tSA7EHvfZ/arcgis/rest/services/California_Fire_Perimeters/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson")%>%
  st_transform('EPSG:2225')

fire_perimeter <- fire %>% filter(YEAR_=="2010"|YEAR_=="2011"|YEAR_=="2012"|YEAR_=="2013"|YEAR_=="2014"|YEAR_=="2015"|YEAR_=="2016"|YEAR_=="2017"|YEAR_=="2018"|YEAR_=="2019"|YEAR_=="2020")

ggplot() +
  geom_sf(data = fire_perimeter, fill="red", color="transparent")+
 geom_sf(data=ca_counties, fill="transparent")+ 
  labs(title="California Wildfires",
       subtitle="Years 2010-2020")+
  mapTheme()

# fire cases in 2020

fire_2020 <- fire %>% filter(YEAR_=="2020")

ggplot() +
  geom_sf(data = fire_2020, fill="magenta", color="transparent")+
 geom_sf(data=ca_counties, fill="transparent")+ 
  labs(title="California Wildfires",
       subtitle="Years 2020")+
  mapTheme()

# Zoom in North California

N_California <- st_read("https://opendata.arcgis.com/datasets/a61c138d0a6946da8d1ebb8d1c9db13a_0.geojson") %>%
  filter(COUNTY_NAME == 'Del Norte' | COUNTY_NAME == 'Siskiyou' | COUNTY_NAME == 'Humboldt'| COUNTY_NAME == 'Trinity'| COUNTY_NAME == 'Modoc'| COUNTY_NAME == 'Shasta'| COUNTY_NAME == 'Lassen'|COUNTY_NAME == 'Plumas' | COUNTY_NAME == 'Tehama' | COUNTY_NAME == 'Mendocino' | COUNTY_NAME == 'Glenn' |COUNTY_NAME == 'Lake' | COUNTY_NAME == 'Colusa' | COUNTY_NAME == 'Butte' |COUNTY_NAME == 'Sutter'|COUNTY_NAME == 'Yuba' |COUNTY_NAME == 'Sierra' |COUNTY_NAME == 'Nevada' |COUNTY_NAME == 'Placer' |COUNTY_NAME == 'El Dorado' |COUNTY_NAME == 'Sacramento'| COUNTY_NAME == 'Sonoma' |COUNTY_NAME == 'Napa'| COUNTY_NAME == 'Yolo'|COUNTY_NAME == 'Solano') %>%
  st_transform('EPSG:2225')

# Filter Northern California fire
  
N_fire <- st_join(fire_perimeter, N_California, join = st_intersects,left = FALSE)
N_fire2020 <- st_join(fire_2020, N_California, join = st_intersects,left = FALSE)

# convert the date format -- fire records in 2020 are from Feb. 14 to DEC.30
msValue1 = N_fire2020$ALARM_DATE
N_fire2020 <- N_fire2020 %>%
  mutate(ALARM_DATE = as.character(as.POSIXct(msValue1/1000, origin="1970-01-01")))

msValue2 = N_fire2020$CONT_DATE
N_fire2020 <- N_fire2020 %>%
  mutate(CONT_DATE = as.character(as.POSIXct(msValue2/1000, origin="1970-01-01")))

## Wildfire in North California Boundary
ggplot() +
  geom_sf(data = N_fire2020, fill="red", color="transparent")+
  geom_sf(data=N_California, fill="transparent", color="grey", size=0.5)+
  labs(title="North California Wildfires2020",
       subtitle="Years 2020; North California Wildfire")+
  mapTheme()

```

### 2.2 Create Fishnet of Northen California wildfires

create fishnet and combine the vegetation, aspect, elevation, slope data in ArcGIS.


```{r Fishnet, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results=FALSE}

all_data <- read_sf('data\\all_data')%>%
  st_transform('EPSG:2225')%>%
  mutate(uniqueID = JOIN_FID_1 + 1,"County"= NAME, "HAZ_type" = HAZ_DESC, "Vegetation" = WHR13NAME1, "Aspect" = gridcode, "Elevation" = GRIDCODE_1, "Slope" = gridcode11)

fishnet <- all_data%>%
  select(uniqueID,County,HAZ_type,Vegetation,Aspect,Elevation,Slope,geometry)

N_fire1 <- N_fire2020%>%
  dplyr::select(geometry)%>%
  mutate(countfire = 1)

fire_net <- st_join(st_centroid(fishnet), N_fire1, join = st_intersects,left = FALSE)%>% 
  st_drop_geometry()

fire_net2020 <- left_join(fishnet, fire_net, by = "uniqueID")%>%
  dplyr::select(uniqueID, County.x, HAZ_type.x, Aspect.x, Elevation.x, Slope.x, geometry, countfire)

fire_net2020[is.na(fire_net2020)] = 0

firenet2020 <- fire_net2020 %>% 
  group_by(uniqueID) %>% 
  summarise(counts = sum(countfire))
  firenet20 <- firenet2020 %>% mutate(fire = ifelse(counts == "0", "NO_FIRE", 
                                           "FIRE"),"uniqueID" = fishnet$uniqueID,"County" = fishnet$County, "HAZ_type" = fishnet$HAZ_type, "Vegetation" = fishnet$Vegetation, "Aspect" = fishnet$Aspect, "Elevation" = fishnet$Elevation, "Slope" = fishnet$Slope, "geometry" = fishnet$geometry )

ggplot()+
  geom_sf(data = firenet20, aes(fill=fire), color=NA)

  mapTheme()
  

  
```

### 2.3 Load Features

```{r Features, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results=FALSE}
## 1. Powerline
e_stransmission<- st_read("data//California_Electric_Transmission_Lines.geojson") %>%
  st_transform('EPSG:2225')%>%
    st_transform(st_crs(fire_net2020)) %>%
    dplyr::select(geometry)

e_net <- st_join(fishnet, e_stransmission, join = st_intersects,left = FALSE)%>%
  mutate(e = 1)%>%
  group_by(uniqueID) %>% 
  summarise(e_number = sum(e))
e_net <- e_net%>%st_drop_geometry()

e_net1 <- left_join(fishnet, e_net, by = "uniqueID")

e_net1[is.na(e_net1)] = 0

Enet <- e_net1 %>% 
  mutate(e_number = ifelse(e_number == "0", "no_powerline", "powerline"))%>%
  rename("Powerline" = e_number)%>%
  select(uniqueID, Powerline)%>%
  st_drop_geometry()

## 2. Historical Fire (area)

fire_records <- st_join(fire_perimeter, N_California, join = st_intersects,left = FALSE)%>%
  filter(YEAR_=="2015"|YEAR_=="2016"|YEAR_=="2017"|YEAR_=="2018"|YEAR_=="2019")%>%
  mutate(firerecord = 1)%>%
  dplyr::select(geometry,firerecord)

records_net <- st_join(st_centroid(fishnet), fire_records, join = st_intersects,left = FALSE)%>% 
  st_drop_geometry()

Historical_Fire <- left_join(fishnet, records_net, by = "uniqueID")%>%
  dplyr::select(uniqueID, County.x, HAZ_type.x, Aspect.x, Elevation.x, Slope.x, geometry, firerecord)

Historical_Fire[is.na(Historical_Fire)] = 0

Historical_Fire <- Historical_Fire %>% 
  group_by(uniqueID) %>% 
  summarise(firerecordcounts = sum(firerecord))  

Historical_Fire <- Historical_Fire %>% st_drop_geometry()

firenet20_his <- cbind (firenet20,Historical_Fire,Enet)%>%rename("his_counts" = firerecordcounts) %>% select(-uniqueID.1,-uniqueID.2)

## 3. Weather

#riem_networks()
#ca_stations = riem_stations("CA_ASOS")
#ca_stations2 <- st_as_sf(ca_stations, coords = c("lon", "lat"), crs = 4326)

weather_station_ids <- c("SIY", "CEC", "MHS", "O86", "ACV", "FOT", "RDD", "RBL", "CIC", "OVE","UKI", "MYV", "STS", "O69", "DVO", "APC", "SUU", "VCB", "EDU", "SMF", "LHM", "MYV", "AAT", "SVE", "PVF", "AUN","SAC", "MCC", "CIC","JAQ","MHR")

# df - stations with lat/lon and name info (in addition to ids)
asos_socal_stations <- riem_stations("CA_ASOS") %>% filter(str_detect(id, paste(weather_station_ids, collapse="|")))
asos_socal_stations$weather_station_id <- asos_socal_stations$id
asos_socal_stations <-  st_as_sf(asos_socal_stations, coords = c("lon","lat"), crs = 4326, agr = "constant") %>% st_transform('EPSG:2225')
asos_socal_stations$weather_ID <-  seq.int(nrow(asos_socal_stations))

## Finding closest station
weather_coords <- 
  asos_socal_stations %>%
  select(geometry)

st_c <- st_coordinates
st_coid <- st_centroid

closest_weather_station_to_fishnet <- nn2(st_c(weather_coords), st_c(st_coid(fishnet)), k = 1)$nn.idx

firenet20_his$weather_ID <- closest_weather_station_to_fishnet

#ggplot()+
  #geom_sf(data = N_California)+
  #geom_sf(data = weather_coords)

get_weather_features_by_station <- function(weather_station_ids, start_year, end_year){
  
  year_vec <- seq(start_year, end_year)
  i <- 1
  weather_data_list <- list()
  for(station_id in weather_station_ids){
    print(paste("Processing station", station_id))
    for(year in year_vec){
      start_date = paste0(year, "02-14")
      end_date = paste0(year, "12-30")
      weather_data <- riem_measures(station = station_id, date_start = start_date, date_end = end_date) %>% 
        dplyr::summarise(weather_station_id = station_id,
                         year = year,
                         Max_Temp = max(tmpf, na.rm = TRUE),
                         Mean_Temp = mean(tmpf, na.rm = TRUE),
                         Mean_Precipitation = mean(p01i, na.rm = TRUE),
                         Mean_Humidity = mean(relh, na.rm = TRUE),
                         Mean_Wind_Speed = mean(sknt, na.rm = TRUE),
        ) 
      weather_data_list[[i]] <- weather_data
      i <- i + 1
    }
  }
  
  do.call("rbind", weather_data_list) 
}

weather_data2020 <- get_weather_features_by_station(weather_station_ids, 2020, 2020) %>%
  rename(Max_Temp20 = Max_Temp,
         Mean_Temp20 = Mean_Temp,
         Mean_Precipitation20 = Mean_Precipitation,
         Mean_Humidity20 = Mean_Humidity,
         Mean_Wind_Speed20 = Mean_Wind_Speed)

weather_2020 <- left_join(weather_data2020, asos_socal_stations, on = 'weather_station_id') %>%
  select (-weather_station_id, -id, -name, -year, -geometry) %>%
  distinct() 

alldataset2020 <- left_join(firenet20_his, weather_2020, on = "weather_ID")


```

## III Feature Engineering

### 3.1 

Here, we mutated slope and aspects into more clear categories.

```{r Features, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results=FALSE}

# Aspect
engineeredData <-
  alldataset2020 %>%
  mutate(Aspect = case_when(
    Aspect == -1 ~ "Flat",
    Aspect >= 0 & Aspect <= 22.5 ~"North",
    Aspect > 22.5 & Aspect <= 67.5 ~"Northeast",
    Aspect > 67.5 & Aspect <= 112.5 ~"East",
    Aspect > 112.5 & Aspect <= 157.5 ~"Southeast",
    Aspect > 157.5 & Aspect <= 202.5 ~"South",
    Aspect > 202.5 & Aspect <= 247.5 ~"Southwest",
    Aspect > 247.5 & Aspect <= 292.5 ~"West",
    Aspect > 292.5 & Aspect <= 337.5 ~"Northwest",
    Aspect > 337.5 & Aspect <= 360 ~"North"))

# land cover
engineeredData <-
  engineeredData %>%
    mutate(Vegetation = case_when(
    Vegetation == "Conifer Woodland" ~ "Conifer Woodland",
    Vegetation == "Hardwood Forest"  ~ "Hardwood Forest",
    Vegetation == "Shrub"  ~ "Shrub",
    Vegetation == "Agriculture"  ~ "Agriculture",
    Vegetation == "Wetland" |Vegetation == "Water"|Vegetation == "Urban" |Vegetation == "Herbaceous"|
      Vegetation == "Hardwood Woodland" |Vegetation == "Desert Shrub"|Vegetation == "Conifer Forest" |Vegetation == "Barren/Other"  ~ "Other"))


# Exploratory Analysis
## continuous features
engineeredData %>% st_drop_geometry() %>%
  dplyr::select(fire, Elevation, Slope,Max_Temp20, Mean_Temp20,Mean_Humidity20,
                Mean_Precipitation20,Mean_Wind_Speed20) %>%
  gather(Variable, value, -fire) %>%
  ggplot(aes(fire, value, fill=fire)) + 
  geom_bar(position = "dodge", stat = "summary", fun = "mean") + 
  facet_wrap(~Variable, scales = "free") +
  scale_fill_manual(values = palette2) +
  labs(x="Fire", y="Mean", 
       title = "Feature associations with the likelihood of Wildfire",
       subtitle = "(continous Features)") +
  theme(legend.position = "none")

## categorical features
engineeredData %>%st_drop_geometry()%>%
    dplyr::select(fire,HAZ_type,Vegetation, Aspect, his_counts, Powerline) %>%
    gather(Variable, value, -fire) %>%
    count(Variable, value, fire) %>%
      ggplot(., aes(value, n, fill = fire)) +   
        geom_bar(position = "dodge", stat="identity") +
        facet_wrap(~Variable, ncol = 3, scales="free") +
        scale_fill_manual(values = c("#99CCCC","#FFCC99"),
                          name = "Took Credit") +
        labs(x="Took Credit", y="Value",
             title = "Feature associations with the likelihood of Wildfire",
             subtitle = "(Categorical Features)",
       caption = 'Figure 2.2.2-2') +
        theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
## HAZ_type
palette6 <- c("#f7fcf5", "#e5f5e0", "#c7e9c0", "#a1d99b", "#74c476", "#41ab5d")
  
ggplot() +
geom_sf(data = engineeredData, aes(fill = HAZ_type),color= "transparent")+
geom_sf(data = N_fire2020, fill="transparent", color="red")+
scale_fill_manual(values = palette6, name="HAZ_type") +
labs(title="Wildlife Urban Interface and Fire",
     subtitle = "Red outline denotes fire perimeters 2020") +
  mapTheme()

## Vegetation
palatte_nlcd <- c("#aec3d4", "#33510d", "#e2720f", "#369b47", "#30eb5b")
  
ggplot() +
geom_sf(data = engineeredData, aes(fill = Vegetation),color= "transparent")+
geom_sf(data = N_fire2020, fill="transparent", color="black",size = 0.5)+
scale_fill_manual(values = palatte_nlcd, name="Vegetation") +
labs(title="Vegetation and Fire",
     subtitle = "Black outline denotes fire perimeters 2020") +
  mapTheme()

## Aspect
palatte_10 <- c("#aec3d4", "#33510d", "#e2720f", "#369b47", "#30eb5b", "#387242", "#ff6100", "#c3aa69", "#b76031", "#d9903d")
  
#ggplot() +
#geom_sf(data = engineeredData, aes(fill = Aspect),color= "transparent")+
#geom_sf(data = N_fire2020, fill="transparent", color="black",size = 0.5)+
#scale_fill_manual(values = palatte_10, name="Aspect") +
#labs(title="Aspect and Fire",
     #subtitle = "Black outline denotes fire perimeters 2020") +
  #mapTheme()


## correlation between continuous features
numericVars <- select_if(engineeredData , is.numeric) %>% na.omit() %>% st_drop_geometry() %>%
  dplyr::select(Elevation, Slope,Max_Temp20, Mean_Temp20,Mean_Humidity20,
                Mean_Precipitation20,Mean_Wind_Speed20)

ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  colors = c("#25CB10", "white", "#FA7800"),
  type="lower",
  insig = "blank") +  
  labs(title = "Correlation across Characteristics") 

engineeredData <-
  engineeredData %>% mutate(fire_numeric = ifelse(counts == "0", 0, 1))

```

## VI Model Building

### 4.1 

```{r Model, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results=FALSE}
# split the data
set.seed(777)
trainIndex <- createDataPartition(engineeredData$fire, p = .65,
                                 y = paste(
                                   engineeredData$HAZ_type,
                                   engineeredData$Vegetation,
                                   engineeredData$Aspect,
                                   engineeredData$powerline),
                                  list = FALSE,
                                  times = 1)

fireTrain <- engineeredData[ trainIndex,] %>% st_drop_geometry()
fireTest  <- engineeredData[-trainIndex,] %>% st_drop_geometry()

# Model
fireModel <- glm(fire_numeric~ .,
                    data=fireTrain %>% 
                      dplyr::select(-uniqueID,-counts,-weather_ID, -fire),
                    family="binomial" (link="logit"))

summary(fireModel)
pR2(fireModel)


# ROC Curve
## This us a goodness of fit measure, 1 would be a perfect fit, .5 is a coin toss
testProbs <- data.frame(Outcome = as.factor(fireTest$fire_numeric),
                        Probs = predict(fireModel, fireTest, type= "response"))

auc(testProbs$Outcome, testProbs$Probs)

ggplot(testProbs, aes(d = as.numeric(testProbs$Outcome), m = Probs)) +
  geom_roc(n.cuts = 50, labels = FALSE, colour = "#FE9900") +
  style_roc(theme = theme_grey) +
  geom_abline(slope = 1, intercept = 0, size = 1.5, color = 'grey') +
  labs(title = "ROC Curve")

#Distribution of Predicted Probabilities
ggplot(testProbs, aes(x = Probs, fill = as.factor(Outcome))) + 
  geom_density() +
  facet_grid(Outcome ~ .) +
  scale_fill_manual(values = palette2) +
  labs(x = "Fire", y = "Density of probabilities",
       title = "Distribution of predicted probabilities by observed outcome",
       subtitle = "First Model") +
  theme(strip.text.x = element_text(size = 18),
        legend.position = "none")

# Histograms fire
testProbsFire <- testProbs %>% filter (Outcome=="1")
testProbsNoFire <- testProbs %>% filter (Outcome=="0")

hist(testProbsFire$Probs, 
     col="#F96167",
       main="Predicted Probabilities for Grid Cells with Fire",
     xlab="Probability")

# Histograms nofire
hist(testProbsNoFire$Probs, 
     col="#FCE77D",
       main="Predicted Probabilities for Grid Cells with No Fire",
     xlab="Probability")

mean(testProbsNoFire$Probs)
mean(testProbsFire$Probs)

# Confusion Matrix
testProbs <- 
  testProbs %>%
  mutate(predOutcome  = as.factor(ifelse(testProbs$Probs > 0.3, 1, 0)))

caret::confusionMatrix(testProbs$predOutcome, testProbs$Outcome, 
                       positive = "1")


ctrl <- trainControl(method = "cv", number = 100, classProbs=TRUE, summaryFunction=twoClassSummary)

cvFit <- train(fire ~ ., data = engineeredData %>% st_drop_geometry() %>%
                 dplyr::select(-uniqueID,-counts,-weather_ID, -fire_numeric)%>%na.omit(),
               method="glm", family="binomial",
               metric="ROC", trControl = ctrl)

cvFit

dplyr::select(cvFit$resample, -Resample) %>%
  gather(metric, value) %>%
  left_join(gather(cvFit$results[2:4], metric, mean)) %>%
  ggplot(aes(value)) + 
  geom_histogram(bins=35, fill = "#FF006A") +
  facet_wrap(~metric) +
  geom_vline(aes(xintercept = mean), colour = "#981FAC", linetype = 3, size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  labs(x="Goodness of Fit", y="Count", title="CV Goodness of Fit Metrics",
       subtitle = "Across-fold mean represented as dotted lines") +
  plotTheme()


```

## V Model Validation
```{r Validation, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results=FALSE}

crossValidate <- function(dataset, id, dependentVariable, indVariables) {
  
  allPredictions <- data.frame()
  cvID_list <- unique(dataset[[id]])
  
  for (i in cvID_list) {
    
    thisFold <- i
    cat("This hold out fold is", thisFold, "\n")
    
    fold.train <- filter(dataset, dataset[[id]] != thisFold) %>% as.data.frame() %>% 
      dplyr::select(id, geometry, indVariables, dependentVariable)
    fold.test  <- filter(dataset, dataset[[id]] == thisFold) %>% as.data.frame() %>% 
      dplyr::select(id, geometry, indVariables, dependentVariable)
    
    regression <-
      glm(fire_numeric ~ ., family = "binomial", 
          data = fold.train %>% 
            dplyr::select(-geometry, -id))
    
    thisPrediction <- 
      mutate(fold.test, Prediction = predict(regression, fold.test, type = "response"))
    
    allPredictions <-
      rbind(allPredictions, thisPrediction)
    
  }
  return(st_sf(allPredictions))
}

reg.vars <- c("County", "HAZ_type", "Vegetation", "Aspect", "Elevation", "Slope", "his_counts",
              "Powerline", "weather_ID", "Max_Temp20", "Mean_Temp20", "Mean_Precipitation20",
              "Mean_Humidity20", "Mean_Wind_Speed20")


reg.spatialCV <- crossValidate(
  dataset = engineeredData,
  id = "County",
  dependentVariable = "fire_numeric",
  indVariables = reg.vars) 

reg.spatialcv <-
  reg.spatialCV %>%
  dplyr::select("cvID" = County, fire_numeric, Prediction, geometry)

fire_clipped <- st_intersection(st_make_valid(fire_perimeter1418),st_make_valid(selected_counties))

ggplot() +
  geom_sf(data = reg.spatialcv, aes(fill = Prediction), color = "transparent")+
  geom_sf(data = N_fire2020, fill = "transparent", color = "red", size=.5)+
  labs(title="Predicted Probabilities and Actual Fires",
       subtitle="Red outline marks perimeter of actual fires")+
  mapTheme()

```

## vi Risk map
```{r map, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, results=FALSE}

testProbs_all <- data.frame(Outcome = as.factor(engineeredData$fire),
                        Probs = predict(fireModel, engineeredData, type= "response"),
                        uniqueID= engineeredData$uniqueID)

testProbs_all <- testProbs_all %>% mutate(Risk_Cat=
                                            case_when(Probs <=.03 ~ "Low",
                                                   Probs > 0.03 & Probs < .2 ~ "Medium",
                                                   Probs >=.2 ~ "High" ))



fishnet_clipped_probs <- left_join(engineeredData, testProbs_all, on = "uniqueID")

palette3 <- c("#B81D13","#008450","#EFB700")

ggplot() +
  geom_sf(data=fishnet_clipped_probs, aes(fill=Risk_Cat), color="transparent")+
  scale_fill_manual(values=palette3, name="Risk Score") +
  labs(title="Predicted Risk Scores Across 13 Northern California Counties")+
  mapTheme()

```






